
# Aggregate Loss Models 

**Chapter description**

This chapter introduces probability models for describing the aggregate (total) claims that arise from a portfolio of insurance contracts. We present two standard modeling approaches, the individual risk model and the collective risk model. Further, we discuss strategies for computing the distribution of the aggregate claims, including exact methods for special cases, recursion, and simulation. Finally, we examine the effects of individual policy modifications such as deductibles, coinsurance, and inflation, on the frequency and severity distributions, and thus on the aggregate loss distribution.

Although not needed to go through the tutorials, some users may wish to download the overheads used in the videos. <button download><a href="https://raw.githubusercontent.com/OpenActTextDev/LDACourse1/main/LDA1.Overheads/LDA1.Chap5.pdf">Download Chapter Five overheads as a .pdf file.</a></button>

## Introduction 

***

**Start with section learning objectives, often taken directly from the book**

In this section, we learned how to:

- Record aggregated losses from an insurance system
- Identify actuarial applications of aggregate loss models

***

####  Video: Introduction to Aggregate Loss Models {-}

<center>

<iframe id="kaltura_player"  src="https://cdnapisec.kaltura.com/p/1660902/sp/166090200/embedIframeJs/uiconf_id/25717641/partner_id/1660902?iframeembed=true&playerId=kaltura_player&entry_id=1_bock2cl4&flashvars[streamerType]=auto&amp;flashvars[localizationCode]=en_US&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=1_1bqvxhby" width="649" height="401" allowfullscreen webkitallowfullscreen mozAllowFullScreen allow="autoplay *; fullscreen *; encrypted-media *"  frameborder="0" title="Kaltura Player"></iframe>

</center>

#### Overheads: Template - Insert Title Here (Click Tab to View) {-}

**Here is an example of coding the overheads**

<div class="tab">
  <button class="tablinks" onclick="openTab(event, 'Chap5IntroA')">A. Basic Terminology</button>
  <button class="tablinks" onclick="openTab(event, 'Chap5IntroB')">B. Motivation</button>
  <button class="tablinks" onclick="openTab(event, 'Chap5IntroC')">C. Models</button>
  <button class="tablinks" onclick="openTab(event, 'Chap5IntroD')">D. Individual Risk Model</button>
  <button class="tablinks" onclick="openTab(event, 'Chap5IntroE')">E. Moments and Generating Functions</button>
  <button class="tablinks" onclick="openTab(event, 'Chap5IntroF')">F. Applications</button>
      </div>

<div id="Chap5IntroA" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap5.pdf#page=3" width="100%" height="400"> </iframe>
  </div>
<div id="Chap5IntroB" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap5.pdf#page=4" width="100%" height="400"> </iframe>
  </div>
<div id="Chap5IntroC" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap5.pdf#page=5" width="100%" height="400"> </iframe>
  </div>
<div id="Chap5IntroD" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap5.pdf#page=7" width="100%" height="400"> </iframe>
  </div>
<div id="Chap5IntroE" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap5.pdf#page=8" width="100%" height="400"> </iframe>
  </div>
<div id="Chap5IntroF" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap5.pdf#page=9" width="100%" height="400"> </iframe>
  </div>


### Exercise. Individual Risk Model

  **Assignment Text**
  
In this assignment, we will revisit Example 5.2.1 in the textbook and reproduce the theoretical results using simulation in `R`.

:::: {.blackbox data-latex=""}
**Instructions**
-  Use the function [rbinom()](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/Binomial) to simulate the number of claims.
-  Use the function [runif()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/Uniform) to claim amounts.
-  You may also check the variations of the simulation results when you use larger or smaller sample sizes for the simulations.
::::
  
  
```{r ex="LDA5.5.3.1", type="hint", tut=TRUE}
Note that we need to simulate claim amounts that corresponds to the number of claims so that the parameters used in `runif()` function may depend on the number of simulated claims.
```


#```{r ex="LDA5.5.3.1", type="pre-exercise-code", tut=TRUE}
#Insample <- read.csv("https://raw.githubusercontent.com/OpenActTextDev/LDACourse1/main/Data/Insample.csv", header=T,
#                     na.strings=c("."), stringsAsFactors=FALSE)
#```


```{r ex="LDA5.5.3.1", type="sample-code", tut=TRUE}
set.seed(1000)     # For reproducibility of results
r  <- 10000        # Number of observations to simulate for each policy
q1 <- 0.05         # Probability of claim from policy 1
m1 <- 0; M1 <- ___ # Parameters for severity distribution X_1
q2 <- ____         # Probability of claim from policy 2
m2 <- _; M2 <- 300 # Parameters for severity distribution X_2
n1 <- ____         # Number of type 1 policies
n2 <- 200          # Number of type 2 policies

S <- rep(NA, r) # Initialize an empty vector to store S observations

n1 <- rbinom(r, size=n1, prob=q1) # Generate r=10000 observations of N1 from Binomial
n2 <- rbinom(r, size=__, prob=__) # Generate r=10000 observations of N2 from Binomial

for(j in 1:r){ 
  x1_j <- runif(n1[j], min=m1, max=M1)
  x2_j <- runif(_____, min=__, max=__)
  s_j  <- sum(x1_j)+sum(___) # Calculate the aggregate loss s_j
  S[j] <- s_j # Store s_j in the vector of observations
}
mean(S) # Compare to theoretical value of 2,800
var(S)  # Compare to theoretical value of 600,467
```


```{r ex="LDA5.5.3.1", type="solution", tut=TRUE}
set.seed(1000)     # For reproducibility of results
r  <- 10000        # Number of observations to simulate for each policy
q1 <- 0.05         # Probability of claim from policy 1
m1 <- 0; M1 <- 400 # Parameters for severity distribution X_1
q2 <- 0.06         # Probability of claim from policy 2
m2 <- 0; M2 <- 300 # Parameters for severity distribution X_2
n1 <- 100          # Number of type 1 policies
n2 <- 200          # Number of type 2 policies

S <- rep(NA, r) # Initialize an empty vector to store S observations

n1 <- rbinom(r, size=n1, prob=q1) # Generate r=10000 observations of N1 from Binomial
n2 <- rbinom(r, size=n2, prob=q2) # Generate r=10000 observations of N2 from Binomial

for(j in 1:r){ 
  x1_j <- runif(n1[j], min=m1, max=M1)
  x2_j <- runif(n2[j], min=m2, max=M2)
  s_j  <- sum(x1_j)+sum(x2_j) # Calculate the aggregate loss s_j
  S[j] <- s_j # Store s_j in the vector of observations
}
mean(S) # Compare to theoretical value of 2,800
var(S)  # Compare to theoretical value of 600,467
```

```{r ex="LDA5.5.3.1", type="sct", tut=TRUE}
success_msg("Getting started is always the hardest thing to do. Excellent start!")
```

**Finish the section with quizzes from the book. We can modify them, if needed.**

```{r child = './Quizzes/Quiz51.html', eval = QUIZ}
```

## Tweedie Distribution 


**Start with section learning objectives, often taken directly from the book**

In this section, we use **zzz**. You learn how to:

- zz
- zz
- zz.

***



####  Video: Tweedie Distributions {-}

<center>

<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/1660902/sp/166090200/embedIframeJs/uiconf_id/25717641/partner_id/1660902?iframeembed=true&playerId=kaltura_player&entry_id=1_lxnu6a93&flashvars[streamerType]=auto&amp;flashvars[localizationCode]=en&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=1_jjd6r5f9" width="649" height="401" allowfullscreen webkitallowfullscreen mozAllowFullScreen allow="autoplay *; fullscreen *; encrypted-media *"  frameborder="0" title="Kaltura Player"></iframe>

</center>



```{r child = './Quizzes/Quiz53.html', eval = QUIZ}
```

