
# Introduction to Loss Data Analytics 

**Chapter description**

This course introduces readers to methods of analyzing insurance data. Section \@ref(Sec:Intro) begins with a discussion of why the use of data is important in the insurance industry. Section \@ref(Sec:PredModApps) gives a general overview of the purposes of analyzing insurance data which is reinforced in the Section \@ref(Sec:LGPIF) case study. Naturally, there is a huge gap between the broad goals summarized in the overview and a case study application; this gap is covered through the methods and techniques of data analysis covered in the rest of the text.

Although not needed to go through the tutorials, some users may wish to download the overheads used in the videos. <button download><a href="https://raw.githubusercontent.com/OpenActTextDev/LDACourse1/main/Overheads/LDA1.Chap1.pdf">Download Chapter One overheads as a .pdf file.</a></button>


## Relevance of Analytics to Insurance Activities  {#Sec:Intro}

***

In this section, you learn how to:

- Summarize the importance of insurance to consumers and the economy
- Describe analytics
- Identify data generating events associated with the timeline of a typical insurance contract

***

####  (Placeholder) Video Overview of Insurance Activities - Yvonne {-}


```{r child = './Quizzes/Quiz11.html', eval = QUIZ}
```

## Insurance Company Operations {#Sec:PredModApps}

***
In this section, you learn how to:

- Describe five major operational areas of insurance companies.
- Identify the role of data and analytics opportunities within the pricing area.

***


#### Video Overview of Insurance Company Operations {-}

<center>

<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/1660902/sp/166090200/embedIframeJs/uiconf_id/25717641/partner_id/1660902?iframeembed=true&playerId=kaltura_player&entry_id=1_zbdyak23&flashvars[streamerType]=auto&amp;flashvars[localizationCode]=en_US&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=1_8q8agp9h" width="649" height="401" allowfullscreen webkitallowfullscreen mozAllowFullScreen allow="autoplay *; fullscreen *; encrypted-media *"  frameborder="0" title="Kaltura Player"></iframe>

</center>

#### Overheads of Insurance Company Operations (Click Tab to View) {-}

<div class="tab">
  <button class="tablinks" onclick="openTab(event, 'InsCompOperationsA')">A. Insurance Company Operations I</button>
  <button class="tablinks" onclick="openTab(event, 'InsCompOperationsB')">B. Insurance Company Operations II</button>
  <button class="tablinks" onclick="openTab(event, 'InsCompOperationsC')">C. Operations – Initiating Insurance</button>
  <button class="tablinks" onclick="openTab(event, 'InsCompOperationsD')">D. Big Data</button>
      </div>

<div id="InsCompOperationsA" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=9" width="100%" height="400"> </iframe>
  </div>
<div id="InsCompOperationsB" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=10" width="100%" height="400"> </iframe>
  </div>
<div id="InsCompOperationsC" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=11" width="100%" height="400"> </iframe>
  </div>
<div id="InsCompOperationsD" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=13" width="100%" height="400"> </iframe>
  </div>


```{r child = './Quizzes/Quiz12.html', eval = QUIZ}
```

## Case Study: Property Fund Introduction {#Sec:LGPIF}

***
In this section, we use the Wisconsin Property Fund as a case study. You learn how to:

- Describe how data generating events can produce data of interest to insurance analysts.
- Produce relevant summary statistics for each variable.
- Describe how these summary statistics can be used to develop the cost of insurance.

***

####  Video Introducing the Wisconsin Property Fund {-}

<center>

<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/1660902/sp/166090200/embedIframeJs/uiconf_id/25717641/partner_id/1660902?iframeembed=true&playerId=kaltura_player&entry_id=1_hoil8k0e&flashvars[streamerType]=auto&amp;flashvars[localizationCode]=en_US&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=1_j4brj49g" width="649" height="401" allowfullscreen webkitallowfullscreen mozAllowFullScreen allow="autoplay *; fullscreen *; encrypted-media *"  frameborder="0" title="Kaltura Player"></iframe>

</center>

#### Overheads of Introducing the Wisconsin Property Fund (Click Tab to View) {-}

<div class="tab">
  <button class="tablinks" onclick="openTab(event, 'PropertyFundIntroA')">A. Wisconsin Property Fund</button>
  <button class="tablinks" onclick="openTab(event, 'PropertyFundIntroB')">B. LGPIF Policyholder A</button>
  <button class="tablinks" onclick="openTab(event, 'PropertyFundIntroC')">C. LGPIF Policyholder B</button>
  <button class="tablinks" onclick="openTab(event, 'PropertyFundIntroD')">D. Property Fund</button>
  <button class="tablinks" onclick="openTab(event, 'PropertyFundIntroE')">E. Claims Frequency - R Code</button>
  <button class="tablinks" onclick="openTab(event, 'PropertyFundIntroF')">F. Claims Frequency (2010)</button>
      </div>

<div id="PropertyFundIntroA" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=15" width="100%" height="400"> </iframe>
  </div>
<div id="PropertyFundIntroB" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=16" width="100%" height="400"> </iframe>
  </div>
<div id="PropertyFundIntroC" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=17" width="100%" height="400"> </iframe>
  </div>
<div id="PropertyFundIntroD" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=18" width="100%" height="400"> </iframe>
  </div>
<div id="PropertyFundIntroE" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=19" width="100%" height="400"> </iframe>
  </div>
<div id="PropertyFundIntroF" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=20" width="100%" height="400"> </iframe>
  </div>


### Exercise. Claim Frequency

**Assignment Text**

The Wisconsin Property Fund data has already been read into a data frame called `Insample`. These data consist of claim experience for fund members over the years 2006-2010, inclusive. It includes the frequency of claims `Freq` as well as the claim year `Year`. The video explored the distribution of the claims frequency for year 2010; in this assignment, we replicate this analysis and conduct a similar investigation for year 2009.


:::: {.blackbox data-latex=""}
**Instructions**. For each year:


-  Use the function [subset()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/subset) to create a smaller data set based on a single year.
-  Define the frequency as a global variable.
-  Use the function [length()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/length) to determine the number of observations in a vector.
-  Use the function [mean()](https://www.rdocumentation.org/packages/base/versions/3.5.0/topics/mean/) to calculate the average.
-  Use the function [table()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/table) to tabulate the frequency distribution.
::::


```{r ex="LDA1.1.3.1", type="hint", tut=TRUE}
Take some time to explore the online `R` documentation.

Note the double equal signs `==` needed for the the `subset()` function.
```


```{r ex="LDA1.1.3.1", type="pre-exercise-code", tut=TRUE}
Insample <- read.csv("https://raw.githubusercontent.com/OpenActTextDev/LDACourse1/main/Data/Insample.csv", header=T,
                      na.strings=c("."), stringsAsFactors=FALSE)
```


```{r ex="LDA1.1.3.1", type="sample-code", tut=TRUE}
#  Analysis for Year 2010
Insample2010 <- subset(Insample, Year==2010)
Freq2010 <- Insample2010$Freq
length(Freq2010)
mean(Freq2010)
table(Freq2010)

#  Analysis for Year 2009
Insample2009 <- ___
Freq2009 <- ___
length(___)
mean(___)
table(___)
```


```{r ex="LDA1.1.3.1", type="solution", tut=TRUE}
#  Analysis for Year 2010
Insample2010 <- subset(Insample, Year==2010)
Freq2010 <- Insample2010$Freq
length(Freq2010)
mean(Freq2010)
table(Freq2010)

#  Analysis for Year 2009
Insample2009 <- subset(Insample, Year==2009)
Freq2009 <- Insample2009$Freq
length(Freq2009)
mean(Freq2009)
table(Freq2009)
```

```{r ex="LDA1.1.3.1", type="sct", tut=TRUE}
success_msg("Getting started is always the hardest thing to do. Excellent start!")
```

## Property Fund Claim Severity 

####  (Placeholder) Video Claim Severity for the Wisconsin Property Fund - Yvonne {-}


### Exercise. Exploring Claim Severities

**Assignment Text**

The Wisconsin Property Fund data covering years 2006-2010 has already been read into a data frame called `Insample`. These data includes the average claim severity `yAvg`. The video explored the distribution of the claims severity for year 2010; in this assignment, we conduct a similar investigation for year 2009.

:::: {.blackbox data-latex=""}
**Instructions** 

-  Use the function [subset()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/subset) twice, once to create a smaller data set based on year 2009 experience and again to restrict consideration to fund members with positive claims.
-  From this subset, define the average claim severity as a global variable.
-  Use the function [length()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/length) to determine the number of members with positive claims.
-  Use the function [summary()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/summary) to calculate several summary statistics.
-  Use the function [hist()](https://www.rdocumentation.org/packages/graphics/versions/3.6.2/topics/hist) to produce histograms that visualize the claim severity distribution. Do this once on the original scale and again on the logarithmic scale. Use the `mfrow` switch in the function [par()](https://www.rdocumentation.org/packages/graphics/versions/3.6.2/topics/par) to set the graphical parameters so that the graphs can be viewed side-by-side to promote comparisons.
::::


```{r ex="LDA1.1.4.1", type="pre-exercise-code", tut=TRUE}
Insample <- read.csv("https://raw.githubusercontent.com/OpenActTextDev/LDACourse1/main/Data/Insample.csv", header=T, na.strings=c("."), stringsAsFactors=FALSE)
```



```{r ex="LDA1.1.4.1", type="hint", tut=TRUE}
The `R` function [log()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/log) defaults to natural logarithms. It can also be used to produce common (base 10) as well as other bases.
```


```{r ex="LDA1.1.4.1", type="sample-code", tut=TRUE}
Insample2009 <- ___
InsamplePos2009 <- subset(Insample2009, yAvg>0)
___ <- InsamplePos2009$yAvg

# Table
summary(___)
___(AvgClaim)

# Figures
par(mfrow=c(1, ___))
hist(AvgClaim, main="", xlab="Average Claims")
hist(___, main="", xlab="Logarithmic Average Claims")
```

```{r ex="LDA1.1.4.1", type="solution", tut=TRUE}
Insample2009<- subset(Insample, Year==2009)
InsamplePos2009<- subset(Insample2009, yAvg>0)
AvgClaim <- InsamplePos2009$yAvg

# Table
summary(AvgClaim)
length(AvgClaim)

# Figures
par(mfrow=c(1, 2))
hist(AvgClaim, main="", xlab="Average Claims")
hist(log(AvgClaim), main="", xlab="Logarithmic Average Claims")

```

```{r ex="LDA1.1.4.1", type="sct", tut=TRUE}
success_msg("Excellent! This exercise features data manipulation (through subsetting), calculates summary statistics, and portrays data graphically. You have done it all!")
```


### Exercise. Skewness of the Claim Severity Distribution

**Assignment Text**

Many distributions used in insurance analytics are skewed. In this assignment, we demonstrate how to detect the skewness and show that skewness is a feature of an entire data set, not the result of a handful of outlying observations. Specifically, we consider the average claim for year 2010 of the Wisconsin Property Fund data that has been made available in the variable `AvgClaim`; this variable is only for fund members with positive claims. The video remarked on the skewness of this variable and used a logarithmic transformation to facilitate the analysis. In this assignment, we show how an alternative strategy, omitting unusually large observations, does not address the skewed nature of the distribution.

:::: {.blackbox data-latex=""}
**Instructions**

-  Use the functions [mean()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean) and [median()](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/median) to compute both the mean and median of `AvgClaim`. You will see that the mean is much larger than the median, a classic diagnostic approach for establishing the right skewness of a distribution.
-  Use the function [order()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/order) to order the data in terms of decreasing size.
-  Use the function [head()](https://www.rdocumentation.org/packages/utils/versions/3.6.2/topics/head) to examine the 10 largest observations.
-  Create 6 histograms, graphically presenting them in panels that have 2 rows and 3 columns. In the first histogram, omit the 9 largest observations. In the second, omit the 6 largest. Continuing this pattern, omit 5 in the third histogram, omit 3 in the fourth, omit 1 in the fifth, and do not admit any in the sixth. A careful inspection of this panel of histograms reveals that the distribution remains skewed, despite repeatedly removing large outlying observations.
::::



```{r ex="LDA1.1.4.2", type="pre-exercise-code", tut=TRUE}
Insample <- read.csv("https://raw.githubusercontent.com/OpenActTextDev/LDACourse1/main/Data/Insample.csv", header=T,
                      na.strings=c("."), stringsAsFactors=FALSE)
Insample2010<- subset(Insample, Year==2010)
InsamplePos2010<- subset(Insample2010, yAvg>0)
AvgClaim <- InsamplePos2010$yAvg
```



```{r ex="LDA1.1.4.2", type="hint", tut=TRUE}
The syntax `x[order(x)]` produces an (increasing) ordered version of a vector `x`.
```


```{r ex="LDA1.1.4.2", type="sample-code", tut=TRUE}
mean(___)
___(AvgClaim)

Order.AvgClaim <- AvgClaim[___(AvgClaim, decreasing = TRUE)]
head(Order.AvgClaim, n = ___)

# Figures
par(mfrow=c(2,3))
hist(Order.AvgClaim[-c(1:9)], main="", xlab="Claims - Drop 9")
hist(Order.AvgClaim[___], main="", xlab="Claims - Drop 6")
___(Order.AvgClaim[-c(1:5)], main="", xlab="Claims - Drop 5")
hist(Order.AvgClaim[-c(1:3)], main="", xlab="Claims - Drop 3")
hist(Order.AvgClaim[-1], main="", xlab="Claims - Drop 1")
hist(Order.AvgClaim, main="", xlab="Claims - All")
```

```{r ex="LDA1.1.4.2", type="solution", tut=TRUE}
mean(AvgClaim)
median(AvgClaim)

Order.AvgClaim <- AvgClaim[order(AvgClaim, decreasing = TRUE)]
head(Order.AvgClaim, n = 10)

# Figures
par(mfrow=c(2,3))
hist(Order.AvgClaim[-c(1:9)], main="", xlab="Claims - Drop 9")
hist(Order.AvgClaim[-c(1:6)], main="", xlab="Claims - Drop 6")
hist(Order.AvgClaim[-c(1:5)], main="", xlab="Claims - Drop 5")
hist(Order.AvgClaim[-c(1:3)], main="", xlab="Claims - Drop 3")
hist(Order.AvgClaim[-1], main="", xlab="Claims - Drop 1")
hist(Order.AvgClaim, main="", xlab="Claims - All")
```


```{r ex="LDA1.1.4.2", type="sct", tut=TRUE}
success_msg("Excellent! Removing large unusual observations has its place in statistics. However, in insurance analytics, large observations are not unusual for distributions that are skewed. Removing large observations is not a technique that changes the skewed nature of these distributions.")
```

***


### Exercise. Claim Severity by Year

**Assignment Text**

Much of insurance analytics is about making predictions of future behavior. To understand distributions in future years, we look at *trends* in distributions from the current and preceding years. Some simple trends that are helpful not only for understanding but also communicating results to others involve looking at mean, or average, behavior. In this assignment, we examine 2006-2010 of the Wisconsin Property Fund that has been previously load into the data frame `Insample`. As in the video, by `Year` we calculate mean values of claims frequency (`Freq`), average claims severity (`yAvg`) and coverage (`BCcov`), as well as the number of fund members.

:::: {.blackbox data-latex=""}
**Instructions**

-  Use the function [ddply()](https://www.rdocumentation.org/packages/plyr/versions/1.8.6/topics/ddply) to produce a data frame with the requisite summary statistics.
-  To document results, provide intuitive names of these summary statistics.
::::


```{r ex="LDA1.1.4.3", type="pre-exercise-code", tut=TRUE}
Insample <- read.csv("https://raw.githubusercontent.com/OpenActTextDev/LDACourse1/main/Data/Insample.csv", header=T,
                      na.strings=c("."), stringsAsFactors=FALSE)
```


```{r ex="LDA1.1.4.3", type="hint", tut=TRUE}
The syntax `x[order(x)]` produces an (increasing) ordered version of a vector `x`.
```


```{r ex="LDA1.1.4.3", type="sample-code", tut=TRUE}
library(___)
Table1In <- ddply(Insample, c("Year"), summarize,
               AvgFreq    = mean(Freq), AvgSev = ___(yAvg),
               AvgCov   = ___(BCcov), NumPol = ___(Freq) )
names(Table1In) <- c("Year", "Average Frequency",
                     "Average Severity", "Average Coverage",
                     "Number of Policyholders")
Table1In
```

```{r ex="LDA1.1.4.3", type="solution", tut=TRUE}
library(plyr)
Table1In <- ddply(Insample, c("Year"), summarize,
               AvgFreq    = mean(Freq), AvgSev = mean(yAvg),
               AvgCov   = mean(BCcov), NumPol = length(Freq) )
names(Table1In) <- c("Year", "Average Frequency",
                     "Average Severity", "Average Coverage",
                     "Number of Policyholders")
Table1In
```

```{r ex="LDA1.1.4.3", type="sct", tut=TRUE}
success_msg("Excellent!")
```


## Property Fund Rating Variables 

#### Video Overview of Rating Variables for the Wisconsin Property Fund {-}

<center>

<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/1660902/sp/166090200/embedIframeJs/uiconf_id/25717641/partner_id/1660902?iframeembed=true&playerId=kaltura_player&entry_id=1_her84m65&flashvars[streamerType]=auto&amp;flashvars[localizationCode]=en_US&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=1_6kmvke4f" width="649" height="401" allowfullscreen webkitallowfullscreen mozAllowFullScreen allow="autoplay *; fullscreen *; encrypted-media *"  frameborder="0" title="Kaltura Player"></iframe>

</center>

#### Overheads of Rating Variables for the Wisconsin Property Fund (Click Tab to View) {-}

<div class="tab">
  <button class="tablinks" onclick="openTab(event, 'RatingVariablesA')">A. Description of Rating Variables</button>
  <button class="tablinks" onclick="openTab(event, 'RatingVariablesB')">B. Claims by Entity Type, Fire Class, and No Claim Credit</button>
  <button class="tablinks" onclick="openTab(event, 'RatingVariablesC')">C. Claim Frequency and Severity, Deductibles, and Coverage -
R Code</button>
  <button class="tablinks" onclick="openTab(event, 'RatingVariablesD')">D. Claims by Entity Type and Alarm Credit Category</button>
  <button class="tablinks" onclick="openTab(event, 'RatingVariablesE')">E. Initiating Insurance</button>
</div>

<div id="RatingVariablesA" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=30" width="100%" height="400"> </iframe>
  </div>
<div id="RatingVariablesB" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=31" width="100%" height="400"> </iframe>
  </div>
<div id="RatingVariablesC" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=32" width="100%" height="400"> </iframe>
  </div>
<div id="RatingVariablesD" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=33" width="100%" height="400"> </iframe>
  </div>
<div id="RatingVariablesE" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  ![](./Overheads/LDA1.Chap1.pdf#page=34){width="100%" height="400"}
  </div>
  
  
  
### Exercise. Claim by Entity Type, Fire Class, and No Claim Credit

**Assignment Text**

Analytics of insurance data has much in common with analytics in other areas but insurance also has its own peculiarities. One of example of this is how one only examines summary statistics for positive claims. (Mathematically, the claim severity distribution is defined conditional on the occurrence of a claim). As a consequence, we often need to write specialized routines for insurance applications.

Your supervisor finds useful the analysis completed of claims outcomes by entity type, fire class, and no claim code. To make this analysis more impactful, the supervisor wants you to modify the code to include a basic measure of uncertainty, the standard deviation.

:::: {.blackbox data-latex=""}
**Instructions**

-  Modify the function created for this specific analysis, `ByVarSumm`, to include the standard deviation statistic. Note that, like the mean, we only calculate the standard deviation on the sub-sample of positive claims.
-  Include documentation of this standard deviation statistic in the table.
::::


```{r ex="LDA1.1.5.1", type="pre-exercise-code", tut=TRUE}
Insample <- read.csv("https://raw.githubusercontent.com/OpenActTextDev/LDACourse1/main/Data/Insample.csv", header=T,
                      na.strings=c("."), stringsAsFactors=FALSE)
```


```{r ex="LDA1.1.4.3", type="hint", tut=TRUE}
To compute standard deviations, you can use the function [sd()](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/sd).
```


```{r ex="LDA1.1.5.1", type="sample-code", tut=TRUE}
ByVarSumm <- function(datasub){
  A1 <- length(datasub$Freq)
  A2 <- mean(datasub$Freq)
  datasub1 <-  subset(datasub, yAvg>0)
  A3 <- mean(datasub1$yAvg)
  A4 <- ___ 
  return( c(A1,A2,A3, ___) )
  }

t1 <- ByVarSumm(subset(Insample, TypeVillage == 1))
t2 <- ByVarSumm(subset(Insample, TypeCity == 1))
t3 <- ByVarSumm(subset(Insample, TypeCounty == 1))
t4 <- ByVarSumm(subset(Insample, TypeMisc == 1))
t5 <- ByVarSumm(subset(Insample, TypeSchool == 1))
t6 <- ByVarSumm(subset(Insample, TypeTown == 1))
t7 <- ByVarSumm(subset(Insample, Fire5 == 0))
t8 <- ByVarSumm(subset(Insample, Fire5 == 1))
t9 <- ByVarSumm(subset(Insample, Insample$NoClaimCredit == 0))
t10 <- ByVarSumm(subset(Insample, Insample$NoClaimCredit == 1))
t11 <- ByVarSumm(Insample)

Tablea <- rbind(t1,t2,t3,t4,t5,t6,t7,t8,t9,t10,t11)
Table4 <- round(Tablea, digits = 3)
colnames(Table4) <- c("Number of Policies", "Claim Frequency", 
                      "Average Severity", ___)
rownames(Table4) <- c("Village","City","County","Misc","School",
                      "Town","Fire5--No","Fire5--Yes","NoClaimCredit--No",
                      "NoClaimCredit--Yes","Total")
Table4
```

```{r ex="LDA1.1.5.1", type="solution", tut=TRUE}
ByVarSumm <- function(datasub){
  A1 <- length(datasub$Freq)
  A2 <- mean(datasub$Freq)
  datasub1 <-  subset(datasub, yAvg>0)
  A3 <- mean(datasub1$yAvg)
  A4 <- sd(datasub1$yAvg)  
  return( c(A1,A2,A3,A4) )
  }

t1 <- ByVarSumm(subset(Insample, TypeVillage == 1))
t2 <- ByVarSumm(subset(Insample, TypeCity == 1))
t3 <- ByVarSumm(subset(Insample, TypeCounty == 1))
t4 <- ByVarSumm(subset(Insample, TypeMisc == 1))
t5 <- ByVarSumm(subset(Insample, TypeSchool == 1))
t6 <- ByVarSumm(subset(Insample, TypeTown == 1))
t7 <- ByVarSumm(subset(Insample, Fire5 == 0))
t8 <- ByVarSumm(subset(Insample, Fire5 == 1))
t9 <- ByVarSumm(subset(Insample, Insample$NoClaimCredit == 0))
t10 <- ByVarSumm(subset(Insample, Insample$NoClaimCredit == 1))
t11 <- ByVarSumm(Insample)

Tablea <- rbind(t1,t2,t3,t4,t5,t6,t7,t8,t9,t10,t11)
Table4 <- round(Tablea, digits = 3)
colnames(Table4) <- c("Number of Policies", "Claim Frequency", 
                      "Average Severity", "Std Dev Severity")
rownames(Table4) <- c("Village","City","County","Misc","School",
                      "Town","Fire5--No","Fire5--Yes","NoClaimCredit--No",
                      "NoClaimCredit--Yes","Total")
Table4
```


```{r ex="LDA1.1.5.1", type="sct", tut=TRUE}
success_msg("Excellent! Modifying someone else's code can be more difficult than writing your own. It is a necessary skill when working for large organizations. It also makes you appreciate the value of documenting your own code for future users.")
```


```{r child = './Quizzes/Quiz13.html', eval = QUIZ}
```
