
# Chapter Template - Insert Title Here 

**Chapter description**

**Start with a chapter intro, often taken directly from the book**

***

**Also nice to include a downloadable link to chapter overheads.**

Although not needed to go through the tutorials, some users may wish to download the overheads used in the videos. <button download><a href="https://raw.githubusercontent.com/OpenActTextDev/LDACourse1/main/LDA1.Overheads/LDA1.Chap2.pdf">Download Chapter Two overheads as a .pdf file.</a></button>

***

## Section Template - Insert Title Here 

***

**Start with section learning objectives, often taken directly from the book**

In this section, we use **zzz**. You learn how to:

- zz
- zz
- zz.

***

####  Video: Template - Insert Title Here {-}

**Insert video location here. Right now hosted by UW-Madison**

<center>

<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/1660902/sp/166090200/embedIframeJs/uiconf_id/25717641/partner_id/1660902?iframeembed=true&playerId=kaltura_player&entry_id=1_hoil8k0e&flashvars[streamerType]=auto&amp;flashvars[localizationCode]=en_US&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=1_j4brj49g" width="649" height="401" allowfullscreen webkitallowfullscreen mozAllowFullScreen allow="autoplay *; fullscreen *; encrypted-media *"  frameborder="0" title="Kaltura Player"></iframe>

</center>

#### Overheads: Template - Insert Title Here (Click Tab to View) {-}

**Here is an example of coding the overheads**

<div class="tab">
  <button class="tablinks" onclick="openTab(event, 'ChapTemplateA')">A. Wisconsin Property Fund</button>
  <button class="tablinks" onclick="openTab(event, 'ChapTemplateB')">B. LGPIF Policyholder A</button>
  <button class="tablinks" onclick="openTab(event, 'ChapTemplateC')">C. LGPIF Policyholder B</button>
  <button class="tablinks" onclick="openTab(event, 'ChapTemplateD')">D. Property Fund</button>
  <button class="tablinks" onclick="openTab(event, 'ChapTemplateE')">E. Claims Frequency - R Code</button>
  <button class="tablinks" onclick="openTab(event, 'ChapTemplateF')">F. Claims Frequency (2010)</button>
      </div>

<div id="ChapTemplateA" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=16" width="100%" height="400"> </iframe>
  </div>
<div id="ChapTemplateB" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=17" width="100%" height="400"> </iframe>
  </div>
<div id="ChapTemplateC" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=18" width="100%" height="400"> </iframe>
  </div>
<div id="ChapTemplateD" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=19" width="100%" height="400"> </iframe>
  </div>
<div id="ChapTemplateE" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=20" width="100%" height="400"> </iframe>
  </div>
<div id="ChapTemplateF" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <iframe src="./Overheads/LDA1.Chap1.pdf#page=21" width="100%" height="400"> </iframe>
  </div>


### Exercise. Claim Frequency

**Next include one or two exercises per section. Here is an example.**

**Assignment Text**

The Wisconsin Property Fund data has already been read into a data frame called `Insample`. These data consist of claim experience for fund members over the years 2006-2010, inclusive. It includes the frequency of claims `Freq` as well as the claim year `Year`. The video explored the distribution of the claims frequency for year 2010; in this assignment, we replicate this analysis and conduct a similar investigation for year 2009.


:::: {.blackbox data-latex=""}
**Instructions**. For each year:


-  Use the function [subset()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/subset) to create a smaller data set based on a single year.
-  Define the frequency as a global variable.
-  Use the function [length()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/length) to determine the number of observations in a vector.
-  Use the function [mean()](https://www.rdocumentation.org/packages/base/versions/3.5.0/topics/mean/) to calculate the average.
-  Use the function [table()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/table) to tabulate the frequency distribution.
::::


```{r ex="LDA1.1.3.1", type="hint", tut=TRUE}
Take some time to explore the online `R` documentation.

Note the double equal signs `==` needed for the the `subset()` function.
```


```{r ex="LDA1.1.3.1", type="pre-exercise-code", tut=TRUE}
Insample <- read.csv("https://raw.githubusercontent.com/OpenActTextDev/LDACourse1/main/Data/Insample.csv", header=T,
                      na.strings=c("."), stringsAsFactors=FALSE)
```


```{r ex="LDA1.1.3.1", type="sample-code", tut=TRUE}
#  Analysis for Year 2010
Insample2010 <- subset(Insample, Year==2010)
Freq2010 <- Insample2010$Freq
length(Freq2010)
mean(Freq2010)
table(Freq2010)

#  Analysis for Year 2009
Insample2009 <- ___
Freq2009 <- ___
length(___)
mean(___)
table(___)
```


```{r ex="LDA1.1.3.1", type="solution", tut=TRUE}
#  Analysis for Year 2010
Insample2010 <- subset(Insample, Year==2010)
Freq2010 <- Insample2010$Freq
length(Freq2010)
mean(Freq2010)
table(Freq2010)

#  Analysis for Year 2009
Insample2009 <- subset(Insample, Year==2009)
Freq2009 <- Insample2009$Freq
length(Freq2009)
mean(Freq2009)
table(Freq2009)
```

```{r ex="LDA1.1.3.1", type="sct", tut=TRUE}
success_msg("Getting started is always the hardest thing to do. Excellent start!")
```

**Finish the section with quizzes from the book. We can modify them, if needed.**

```{r child = './Quizzes/Quiz13.html', eval = QUIZ}
```
